---
title: "Homework 9"
author: "Mitchelle Mojekwu"
date: "2022-11-14"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(knitr)
library(readr)
library(tidyverse)
library(broom)
library(readr)
```

#Task 1 Write code in R that uses Newton-Raphson to find the square root
of a number c, i.e., use the function $f(x) = x^2-c$. With $c= 650$ and
a starting point of $x_1=10$, how many steps does it take (i.e. what is
the value of t) for the error in the approximation to first become less
than 0.001?

```{r}

x_t <- 10 #starting point
x_tt <- 100000 #this is x_t+1
t <- 0 #tracks iterations

while(abs(x_tt - x_t) >= 0.001){ #iterate until |x_t+1 - x_t| is less thann 0.001
  if (t>0){
    x_t <- x_tt
  }
  fx <- x_t ^ 2 - 650 #scalar function
  d_fx <- 2*x_t
  x_tt <- x_t -(fx/d_fx) #x_t+1 = x_t - [f(x_t)/f'(x_t)]
  t <- t+1
}
t 
x_t
x_tt
```

As seen above, it takes 5 steps for the error in the approximation to
first become less than 0.001. i.e. $t=5$.

#Task 2

Perform logistic regression to study the probability of failure as a
function of temperature.

```{r ,include=FALSE}
library(alr4)
```

```{r data}
#glimpse(alr4::Challeng)
oring <- alr4::Challeng

#fail: # of o-rings that have failed (failure is when 1 or 2 o-rings fail)
#temp: air temperature at launch (degrees F)

#add factor column where 0=no fail o-rings failed, 1= >0 o-rings failed
oring$fail_fact <-ifelse(oring$fail >0,1,0)
glimpse(oring)
```

```{r}
#Logistic Regression
oring_model <- glm(fail_fact==1 ~ temp, data = oring, family = "binomial")

tidy(oring_model) %>% 
  kable(digits = 3)

```
